Decentralized autonomous organization to automate governance\\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2016-04-08 paper/Paper.tex
style

Crowdfunding (\cite{2015CFReport}) amplifies the problem.  On the one hand, it has made it easier for small contributors to invest in large projects.  It has also made it possible for entrepeneurs to receive financial support that might not have been easily available in the past.  On the other hand, small investors remain vulnerable to financial mismanagement or outright fraud.  Because they have small stakes in a venture, they may lack power to identify problems, participate in governance decisions, or to easily recover their investment.  (\cite{9MostDisgracefulCrowdFundings, CrowdfundingFailTC}).  At the same time, corporate leadership and managment may be accused of malfeasance or mismanagement when they believe that they have acted in good faith, based on their understanding of their obligations and interpretation of applicable rules.

We present a potential solution using Ethereum, (\cite{buterin2013ethereum,Wood2014ethereum}) a blockchain technology which integrates a Turing complete programming language with smart contract processing functionality.  We illustrate a method that for the first time allows the creation of organizations in which (1) ?participants?  maintain direct real-time control of contributed funds and (2) where governance rules are formalized and automated using software.  Specifically, we have written generic smart contract code (\cite{szabo1997formalizing, miller1997future}) that can be used to form a Decentralized Autonomous Organization (DAO) on the Ethereum blockchain. In this paper we explain how the DAO code works.  We do so by focusing on some basic formation and governance features, including formation, funding and voting rights.

@@

\section{Dao Concept | Dao Practice}

@@

Once deployed, the DAO code requires ``ether'' to engage in transactions on Ethereum.  (Ether is the digital fuel that powers the Ethereum network).  Without ether, a DAO can not do very much and a DAO's first order of business is to receive ether.  After the DAO code is deployed, ether may be sent to the DAO?s smart contract address during an initial funding period which is defined in the DAO code.

@@

The DAO stores ether and transmits it based on the DAO code. It does not do much else.  It cannot build a product, write code or develop hardware.  It requires what we have called a "Service Provider'' to accomplish these and other goals.  The DAO engages a Service Provider by accepting a Service Provider proposal.

@@

The integer \verb|rewards| counts all the rewards which have been sent to the DAO. It gets set to zero when paid out to the \verb|rewardAccount|.

@@

The variable \verb|rewardAccount| is of the type \verb|ManagedAccount| , which will be discussed in \ref{app:ManagedAccount}. It is used to manage the rewards which are to be distributed to the DAO Token Holders and reward token holders.

@@

@@

\subsubsection*{payDAO}
This function is used to receive and track the rewards generated by the products funded by the DAO and returns true when ether has been added to \verb|rewards|. In the context of Slock.it, these will be the rewards generated when Slocks are deployed or used.

@@

@@

\subsubsection*{withdrawRewardFor}
This function is used to retrieve the portion of the rewards in the \verb|rewardAccount| which belong to address given in the parameter.
Their portion of the reward tokens $S$ is calculated as follows:
\begin{equation}
 S = R_{\text{DAO}} \cdot T_{\text{sender}} / T_{\text{total}} + R_{\text{sender}}
\end{equation}
Here $R_{\text{DAO}}$ is the amount of reward tokens owned by the DAO, and $T_{\text{sender}}$ the amount of DAO tokens which are directly owned by the sender. $R_{\text{sender}}$ will always be zero except in the case that the sender is a DAO that has split from the original DAO and owns their own reward tokens from the split.
The amount of ether $\Xi_{\text{reward}}$ which is then sent to the DAO token holder that calls this function is:
\begin{equation}
\Xi_{\text{reward}} = \Xi_{\text{rewardAccount}} \cdot S / R_{\text{total}} - \Xi_{\text{paidOut[sender]}}
\end{equation}
Here $\Xi_{\text{rewardAccount}}$ is the total rewards ever received by the \verb|rewardAccount|, $R_{\text{total}}$ is the total amount of reward tokens that have ever been created, regardless of splits (\verb|totalRewardToken|) and $\Xi_{\text{paidOut[sender]}}$ is the total amount of wei which has already been paid out to the DAO token holder calling the function. The reward tokens are further elaborated in section \ref{split}.
\subsubsection*{addAllowedAddress}
This function adds an address to the whitelist, \verb|allowedRecipients|. It can only be executed by the service provider.

@@

Reward tokens are used to divide the ether sent to \verb|rewardAccount| amongst the various DAOs that own reward tokens. Reward tokens are only transferred in the event of a DAO split, they can never be owned by anything other than the original DAO or a “fork” of the original DAO that generated the reward tokens.

Reward tokens are generated when the DAO makes any transaction spending ether (with the exception of sending ether to the \verb|rewardAccount|). When the DAO’s products send ether back to the DAO (for example when a Slock sends $1\%$ of a transaction to the DAO), the ether is held with the rest of the ether that the DAO has, but \verb|rewards| counts all the ether which has been received as rewards. The DAO can use these rewards to fund new proposals or to equally distribute the rewards to the reward token holders (using a proposal which gets voted on by the DAO token holders). Then the token holders of the DAOs that hold reward tokens will be able to claim the ether they have earned for their contribution to the original DAO that issued the reward token. To do this the DAO will send the accumulated rewards to the \verb|rewardAccount| which is held in the \verb|ManagedAccount| contract. Then and only then will the token holders of the DAOs that hold reward tokens be able to call the \verb|getMyReward| function and receive their ether. These payouts are tracked by the map \verb|paidOut| which keeps track of which DAOs hold reward tokens and whether they have claimed their portion of the rewards, and which of the original DAO token holders have claimed their fair portion of the rewards.This process guarantees that any DAO token holder whose ether was spent building a product will receive the rewards promised to them from that product even if they decide to split from the DAO.

@@

\section{Updates}
Although the code of the contract specified at a certain address in the Ethereum blockchain can not be changed, there might still be a need for a single member or the DAO as a whole to change the contracts.
Every single member can always split the DAO as described above and move their funds to a new DAO. From there they can move their funds to another new DAO with a new smart contract.
But in order to use a new code for the complete DAO one can simply create a new DAO contract with all the needed features and deploy it on the blockchain, and make a proposal to send all the ether in the old DAO to this contract.
If accepted, the complete DAO moves to the new contract. In order to use the same underlying DAO tokens there, one can use the \verb|approve| function and give the new DAO the right to move the tokens. In the new contract this right should only be usable in restricted functions which are only callable by the owner of the tokens. This process allows for the DAO to maintain static immutable code on the Ethereum blockchain, while still being able to be updated if the need arises.

>>>>

Crowdfunding (\cite{2015CFReport}) amplifies the problem. On the one hand, it has made it easier for small contributors to invest in large projects. It has also made it possible for entrepeneurs to receive financial support that might not have been easily available in the past. On the other hand, small investors remain vulnerable to financial mismanagement or outright fraud. Because they have small stakes in a venture, they may lack power to identify problems, participate in governance decisions, or to easily recover their investment (\cite{9MostDisgracefulCrowdFundings, CrowdfundingFailTC}). At the same time, corporate leadership and managment may be accused of malfeasance or mismanagement when they believe that they have acted in good faith, based on their understanding of their obligations and interpretation of applicable rules.

We present a potential solution using Ethereum, (\cite{buterin2013ethereum,Wood2014ethereum}) a blockchain technology which integrates a Turing complete programming language with smart contract processing functionality. We illustrate a method that for the first time allows the creation of organizations in which (1) participants maintain direct real-time control of contributed funds and (2) where governance rules are formalized and automated using software. Specifically, we have written generic smart contract code (\cite{szabo1997formalizing, miller1997future}) that can be used to form a Decentralized Autonomous Organization (DAO) on the Ethereum blockchain. In this paper we explain how the DAO code works. We do so by focusing on some basic formation and governance features, including formation, funding and voting rights.

@@

\section{Dao Concept}

@@

Once deployed, the DAO code requires ``ether'' to engage in transactions on Ethereum. Ether is the digital fuel that powers the Ethereum network. Without ether, a DAO can not do very much and a DAO's first order of business is to receive ether. After the DAO code is deployed, ether may be sent to the DAO?s smart contract address during an initial funding period which is defined in the DAO code.

@@

The DAO stores ether and transmits it based on the DAO code. It does not do much else. It cannot build a product, write code or develop hardware. It requires what we have called a ``Service Provider'' to accomplish these and other goals. The DAO engages a Service Provider by accepting a Service Provider proposal.

@@

@@

The variable \verb|rewardAccount| is of the type \verb|ManagedAccount| , which will be discussed in \ref{app:ManagedAccount}. It is used to manage the rewards which are to be distributed to the DAO Token Holders.

Similar, \verb|DAOrewardAccount| is also of the type \verb|ManagedAccount|. This account is used to receive all rewards from projects funded by the DAO. It will then redistribute them amongst all splitted DAOs as well as itself using \verb|retrieveDAOReward|.

@@

Similar, the map \verb|DAOpaidOut| is used to keep track how much a single DAO has already received from \verb|DAOrewardAccount|.

@@

@@

\subsubsection*{newContract}
This function can only be called by the DAO itself (through a proposal and a vote) and is used to move all remaining ether, as well as all rewardTokens to a new address. This is used to update the contract. The new address needs to be approved by the service provider.

@@

\subsubsection*{withdrawRewardFor}
This function is used to retrieve the portion of the rewards in the \verb|rewardAccount| which belong to address given in the parameter.
Their portion of the reward tokens $S$ is calculated as follows:
\begin{equation}
 S = R_{\text{DAO}} \cdot T_{\text{sender}} / T_{\text{total}} + R_{\text{sender}}
\end{equation}
Here $R_{\text{DAO}}$ is the amount of reward tokens owned by the DAO, and $T_{\text{sender}}$ the amount of DAO tokens which are directly owned by the sender. $R_{\text{sender}}$ will always be zero except in the case that the sender is a DAO that has split from the original DAO and owns their own reward tokens from the split.
The amount of ether $\Xi_{\text{reward}}$ which is then sent to the DAO token holder that calls this function is:
\begin{equation}
\Xi_{\text{reward}} = \Xi_{\text{rewardAccount}} \cdot S / R_{\text{total}} - \Xi_{\text{paidOut[sender]}}
\end{equation}
Here $\Xi_{\text{rewardAccount}}$ is the total rewards ever received by the \verb|rewardAccount|, $R_{\text{total}}$ is the total amount of reward tokens that have ever been created, regardless of splits (\verb|totalRewardToken|) and $\Xi_{\text{paidOut[sender]}}$ is the total amount of wei which has already been paid out to the DAO token holder calling the function. The reward tokens are further elaborated in section \ref{split}.

\subsubsection*{retrieveDAOReward}
This function, when called by a DAO, sends the rewards which belong to this DAO from \verb|DAOrewardAccount| to either the DAO itself, or to the \verb|rewardAccount| of the respective DAO in order to be distributed among its token holders, depending on the parameter \verb|_toMembers|.

\subsubsection*{addAllowedAddress}
This function adds an address to the whitelist, \verb|allowedRecipients|. It can only be executed by the service provider.

@@

Reward tokens are used to divide the ether sent to \verb|DAOrewardAccount| amongst the various DAOs that own reward tokens. Reward tokens are only transferred in the event of a DAO split or an update of the contract, they can never be owned by anything other than the original DAO or a “fork” of the original DAO that generated the reward tokens.

Reward tokens are generated when the DAO makes any transaction spending ether. When the DAO’s products send ether back to the DAO (for example when a Slock sends $1\%$ of a transaction to the DAO), the ether is held within \verb|DAOrewardAccount|. The DAO can use these rewards to fund new proposals or to equally distribute the rewards to the reward token holders (using a proposal which gets voted on by the DAO token holders).

Then the token holders of the DAOs will be able to claim the ether they have earned for their contribution to the original DAO that issued the reward token. To do this the DAO retrieve its rewards by callling the \verb|retrieveDAOReward| function, with the paramter \verb|_toMembers| set to true, which send the rewards to the \verb|rewardAccount|b(a \verb|ManagedAccount| contract]. Then and only then will the token holders of the DAOs be able to call the \verb|getMyReward| function and receive their ether.

These payouts are tracked by the map \verb|paidOut| which keeps track of which token holders have claimed their fair portion of the rewards. This process guarantees that any DAO token holder whose ether was spent building a product will receive the rewards promised to them from that product even if they decide to split from the DAO.

@@

\section{Updates}
Although the code of the contract specified at a certain address in the Ethereum blockchain can not be changed, there might still be a need for a single member or the DAO as a whole to change the contracts.
Every single member can always split the DAO as described above and move their funds to a new DAO. From there they can move their funds to another new DAO with a new smart contract.
But in order to use a new code for the complete DAO one can simply create a new DAO contract with all the needed features and deploy it on the blockchain, and make a proposal to call the \verb|newContract| function with the 
If accepted, the complete DAO moves to the new contract. In order to use the same underlying DAO tokens there, one can use the \verb|approve| function and give the new DAO the right to move the tokens. In the new contract this right should only be usable in restricted functions which are only callable by the owner of the tokens. This process allows for the DAO to maintain static immutable code on the Ethereum blockchain, while still being able to be updated if the need arises.
